\todo{How's this title?}A Workflow for Developers New to Web Application Testing

### 2014-06-02 Paper/paper.tex
Thesis meeting edits

\title{\todo{How's this title?}A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications} %\vfill gives us the black space at the top of the page
\author{Taggart Ashby}
\degreemonth{June} \degreeyear{2014} \degree{Master of Science}
\defensemonth{June} \defenseyear{2014}
\numberofmembers{3} \chair{Michael Haungs, Ph.D.} \othermemberA{Franz Kurfess, Ph.D.} \othermemberB{David Janzen, Ph.D.} \field{Computer Science} \campus{San Luis Obispo}
\copyrightyears{seven}

@@

\section{Client/Server Architecture}
Web applications have a user-facing client-side and a ``rear-facing'' \todo{Is this the right term?} server-side.

@@

One example of a client-server architecture that is popular for the web is Representational State Transfer, also known as REST, architecture. If a client-server architecture meets all of the REST criteria, it is said to be RESTful. \todo{Should I really explain all the constraints?} As this paper is not about Client Server interactions, we will not outline the constraints but instead outline how RESTful APIs look in web applications. The RESTful web APIs use: 1) a base URI, 2) an internet media type, and 3) the standard HTTP methods.

@@

\todo{How important is having these? Mention as an option but don't go into detail?}
\subsection{Headless Browsers}
In an attempt to speed up UI testing, which is notoriously slow, there have been efforts to create ``headless'' browsers which behave like normal browsers except that there's no display element. They emulate the DOM and skip the display phase. We opted to stick with visual browsers due to time constraints and the enjoyment of watching the tests execute.

@@

\section{Framework Decision Matrices}
\todo{These are terrible... I have no idea what to put in these tables for columns.}
\FloatBarrier
\begin{table}[h]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Framework & Async Support & Free & Separate Server & Assertion Styles & Test Interfaces & Reporters \\ \hline
Jasmine   & X             & X    &                 &                  &                 &           \\ \hline
Mocha     & X             & X    &                 & X*               & X               & X         \\ \hline
Qunit     & X             & X    &                 &                  &                 &           \\ \hline
Intern    & X             & X    & X               & X                & X               & X         \\ \hline
\end{tabular}
}
\captionof{table}{Decision Matrix for Unit Testing Frameworks}
\end{table}
\FloatBarrier
\footnotesize

@@

\FloatBarrier
\begin{table}[h]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Framework & Free & GitHub & Other Repos & Multi-Language & Online & Beta \\ \hline
Jenkins   & X    & X*     & X*          & X*             & X*     &      \\ \hline
Travis    & X    & X      &             & X              & X      &      \\ \hline
Semaphore &      & X      &             & X              & X      &      \\ \hline
MagnumCI  & X    & X      & X           & X              & X      & X    \\ \hline
Drone.io  & X    & X      & X           & X              & X      &      \\ \hline
\end{tabular}
}
\captionof{table}{Decision Matrix for Continuous Integration Frameworks}
\end{table}
\FloatBarrier

@@

>>>>

% A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications, Developing A Workflow for new Web Developers, 
\title{\todo{How's this title?}A Workflow for Developers New to Web Application Testing} %\vfill gives us the black space at the top of the page
\author{Taggart Ashby}
\degreemonth{June} \degreeyear{2014} \degree{Master of Science}
\defensemonth{June} \defenseyear{2014}
\numberofmembers{3} \chair{Michael Haungs, Ph.D.} \othermemberA{Franz Kurfess, Ph.D.} \othermemberB{David Janzen, Ph.D.} \field{Computer Science} \campus{San Luis Obispo}
\copyrightyears{seven}

@@

\section{Client/Server Architecture}
By their nature, web applications are distributed; they have a client-side and a server-side.

@@

One example of a client-server architecture that is popular for the web is Representational State Transfer, also known as REST, architecture. If a client-server architecture meets all of the REST criteria, it is said to be RESTful. As this paper is not about Client Server interactions, we will not outline the constraints but instead outline how RESTful APIs look in web applications. The RESTful web APIs use: 1) a base URI, 2) an internet media type, and 3) the standard HTTP methods.

@@

\subsection{Headless Browsers}
In an attempt to speed up UI testing, which is notoriously slow, there have been efforts to create ``headless'' browsers which behave like normal browsers except that there's no display element. They emulate the DOM and skip the display phase. We opted to stick with visual browsers due to time constraints and the enjoyment of watching the tests execute.

@@

\section{Framework Decision Matrices}
\todo{What to put in these tables for columns.}
\FloatBarrier
\begin{table}[ht]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Framework & Async Support & Free & Separate Server & Assertion Styles & Test Interfaces & Reporters \\ \hline
Jasmine   & X             & X    &                 &                  &                 &           \\ \hline
Mocha     & X             & X    &                 & X*               & X               & X         \\ \hline
Qunit     & X             & X    &                 &                  &                 &           \\ \hline
Intern    & X             & X    & X               & X                & X               & X         \\ \hline
\end{tabular}
}
\captionof{table}{Decision Matrix for Unit Testing Frameworks}
\end{table}
\FloatBarrier
\footnotesize

@@

\FloatBarrier
\begin{table}[ht]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Framework & Free & GitHub & Other Repos & Multi-Language & Online & Beta \\ \hline
Jenkins   & X    & X*     & X*          & X*             & X*     &      \\ \hline
Travis    & X    & X      &             & X              & X      &      \\ \hline
Semaphore &      & X      &             & X              & X      &      \\ \hline
MagnumCI  & X    & X      & X           & X              & X      & X    \\ \hline
Drone.io  & X    & X      & X           & X              & X      &      \\ \hline
\end{tabular}
}
\captionof{table}{Decision Matrix for Continuous Integration Frameworks}
\end{table}
\FloatBarrier

@@

\section{PolyXpress Tutorial}
\todo{Put the link in with some explanation text}
